\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage{marvosym}
\usepackage[empty]{fullpage}
\usepackage{fancyhdr}
\usepackage[usenames,dvipsnames]{color}
\usepackage{titlesec}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage{tabularx}
\usepackage[hidelinks]{hyperref}
\usepackage[english]{babel}
\usepackage[T1]{fontenc}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\topmargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\textheight}{1in}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}
\setlength{\footskip}{0.5in}

\urlstyle{same}
\pdfgentounicode=1

\titleformat{\section}{
  \scshape\raggedright\large
}{}{0em}{}[\titlerule]

\titlespacing*{\section}{0pt}{0pt}{8pt}

\newcommand{\resumeSubheading}[4]{
  \item
    \begin{tabular*}{0.98\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & {#2} \\
      \textit{\small{#3}} & \textit{\small{#4}}
    \end{tabular*}
    \vspace{-12pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item \vspace{-2pt}
    \begin{tabular*}{0.98\textwidth}{l@{\extracolsep{\fill}}r}
      \small{#1} & {#2}
    \end{tabular*}
    \vspace{-18pt}
}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}}

\newcommand{\resumeItem}[1]{
  \item \small{#1}
}

\renewcommand\labelitemii{\(\vcenter{\hbox{\tiny\(\bullet\)}}\)}

%-------------------------------------------

\begin{document}

% Contact
\begin{center}
  \textbf{\Large \textsc{Yue Cheng}} \\ \vspace{4pt}
  \small 123-456-7890 $|$
  \href{mailto:xx@xx.com}{xx@xx.com} $|$
  \href{https://github.com/xx}{github.com/xx}
\end{center}

% Education
\section{Education}
\resumeSubHeadingListStart
\resumeSubheading
{University of Toronto}{Toronto, Canada}
{Honours Bachelor of Science in Computer Science}{Sep. 2023 -- Present}
\resumeSubheading
{Tongji University}{Shanghai, China}
{Bachelor of Engineering in Industrial Design}{Sep. 2015 -- Jul. 2019}
\resumeSubHeadingListEnd

\vspace{6pt}

% Skills
\section{Skills}
\resumeSubHeadingListStart
\small{\item{
              \textbf{Languages}{: Python, Java, C, HTML/CSS, JavaScript/TypeScript, SQL} \\
              \textbf{Frameworks/Tools}{: React, Next.js, Tailwind CSS, Node.js, GraphQL, MongoDB, Git, Docker, AWS/Azure, Shell, Vim, Regular Expression, Arduino, Processing} \\
              \textbf{Design}{: Office Suite, Adobe Suite, Figma, Sketch, Rhino, Grasshopper, Maya, 3ds Max, AutoCAD} \\
              % \textbf{Soft}{: Design Thinking, Effective Communication, Analytical and Problem Solving, Teamwork and Leadership, Organizational and Time Management}
        }}
\resumeSubHeadingListEnd

% Certificates
% \section{Certificates}
% \resumeSubHeadingListStart
% \small{\item{
%               \textbf{Front-End}{: Meta Front-End Developer Professional Certificate} \\
%               \textbf{Back-End}{: Meta Back-End Developer Professional Certificate}
%         }}
% \resumeSubHeadingListEnd

% Projects
\section{Projects}
\resumeSubHeadingListStart

\resumeProjectHeading
{\textbf{Personal Website} $|$ \emph{Next.js, TypeScript, Tailwind, Framer Motion}}{}
\resumeItemListStart
\resumeItem{Built a \textbf{responsive} personal blog website using \textbf{Next.js}, focusing on delivering a smooth user experience and modern design aesthetics.}
\resumeItem{Implemented \textbf{Contentlayer} for efficient \textbf{data handling}, streamlining content management within the site.}
\resumeItem{Utilized \textbf{Tailwind CSS} and \textbf{Framer Motion} for frontend design, creating a dynamic user interface with responsive animations.}
% \resumeItem{Optimized \textbf{page rendering} by splitting \textbf{font files}, ensuring faster load times and improved performance.}
\resumeItemListEnd

\resumeProjectHeading
{\textbf{Digital Collections Showcase} $|$ \emph{Next.js, TypeScript, Tailwind}}{}
\resumeItemListStart
\resumeItem{Developed a \textbf{book, movie, and music collection showcase} website using \textbf{Next.js}, offering a seamless platform for users to view their collections.}
\resumeItem{Integrated a \textbf{personal API from NeoDB} to fetch and display user-specific data, enhancing the interactivity and personalization of the site.}
\resumeItem{Utilized \textbf{React SWR} to automatically retrieve and update user data, providing real-time information.}
% \resumeItem{Incorporated \textbf{responsive design}, ensuring the site is fully functional across devices.}
\resumeItemListEnd

\resumeProjectHeading
{\textbf{Flowing Metaball} $|$ \emph{Processing, Max/MSP, Grasshopper}}{}
\resumeItemListStart
\resumeItem{Developed a \textbf{parametric spatial design solution}, using \textbf{Processing} and \textbf{Max/MSP} to simulate \textbf{metaball forms} and combine them with functional requirements.}
\resumeItem{Programmed in \textbf{Grasshopper} to automate the generation of \textbf{spatial layouts}, incorporating parameters such as shape, size, and functional needs of the interior space.}
\resumeItem{Awarded \textbf{Best Product Award} in the UNIQLO Design Competition.}
\resumeItemListEnd

\resumeProjectHeading
{\textbf{ Lumosonic} $|$ \emph{Arduino, Leap Motion, MIDI, DMX}}{}
\resumeItemListStart
\resumeItem{Designed an \textbf{interactive game system} that integrates \textbf{open-source hardware} with multimedia art.}
\resumeItem{Utilized \textbf{Leap Motion} to capture hand movements and send data to \textbf{Arduino}, enabling interaction with \textbf{MIDI music software} for dynamic, real-time composition and performance.}
\resumeItem{Integrated \textbf{DMX lighting control} to synchronize \textbf{Par lights} with the music, creating immersive and responsive dynamic lighting effects.}
\resumeItemListEnd

\resumeSubHeadingListEnd

% Experience
\section{Experience}
\resumeSubHeadingListStart
\resumeSubheading
{Research Assistant}{Chongqing, China}
{Chongqing University}{Jan. 2021 -- Mar. 2022}
\vspace{4pt}
\resumeItemListStart
\resumeItem{Developed a demo integrating regional geographic information and conducting spatial asset analysis utilizing \textbf{GIS}, \textbf{NetMiner}, and \textbf{SPSS}.}
\resumeItem{Participated in a national fund research project and a provincial fund research project, co-authored five papers, and contributed to one historical building protection project and two urban planning projects.}
\resumeItem{Attended three academic conferences and co-published one conference paper.}
\resumeItemListEnd
\resumeSubHeadingListEnd

\end{document}
